Tutorial_2a

### 2024-10-27 Tutorial_2a.Rmd
change label in plot priors

# A student-t(df=7.61) prior with scale 1.57 on the logit scale approximates a uniform distribution on the probability scale. This might be a good prior to use for the alpha parameters or Intercept in a logit-hazard model.
pr3 <- tibble(prior = rt(1e6, df = 7.61)* 1.57) %>%  
  ggplot(aes(x = prior)) +
  geom_histogram(bins = 50) +
  scale_y_continuous(NULL, breaks = NULL) +
  annotate(geom="text", x=-12, y=140000, label="t(7.61)*1.57",
              color="red", size=6) +
  annotate(geom = 'text', label = 'C', x = -Inf, y = Inf, hjust = 0, vjust = 1, size=8)+
  theme(panel.grid = element_blank())

>>>>

# A student-t(df=7.61) prior with scale 1.57 on the logit scale approximates a uniform distribution on the probability scale. This might be a good prior to use for the alpha parameters or Intercept in a logit-hazard model.
pr3 <- tibble(prior = rt(1e6, df = 7.61)* 1.57) %>%  
  ggplot(aes(x = prior)) +
  geom_histogram(bins = 50) +
  scale_y_continuous(NULL, breaks = NULL) +
  annotate(geom="text", x=-12, y=140000, label="t(7.61,0,1.57)",
              color="red", size=6) +
  annotate(geom = 'text', label = 'C', x = -Inf, y = Inf, hjust = 0, vjust = 1, size=8)+
  theme(panel.grid = element_blank())
